---
title: "Śledzie"
author: "Urszula Walińska, Julia Będziechowska"
date: '`r format(Sys.Date(), "%d.%m.%Y")`'
output: html_document
---

# Table of contents
1. [Introduction](#introduction)
2. [Some paragraph](#paragraph1)
    1. [Sub paragraph](#subparagraph1)
3. [Another paragraph](#paragraph2)

## This is the introduction <a name="introduction"></a>
Some introduction text, formatted in heading 2 style

## Some paragraph <a name="paragraph1"></a>
The first paragraph text

### Sub paragraph <a name="subparagraph1"></a>
This is a sub paragraph, formatted in heading 3 style

## Another paragraph <a name="paragraph2"></a>
The second paragraph text

```{r, echo=FALSE}
printf <- function(...) invisible(print(sprintf(...)))
```

Repeatable experiment:

```{r}
set.seed(54321)
```

Read data: 

```{r}
data <- read.csv("sledzie.csv")
data <- data[-1]
all_rows_number <- nrow(data)
head(data)
```


```{r}
data[data=="?"] = NA
data<-data[complete.cases(data),]
rows_number <- nrow(data)
```

```{r, echo=FALSE}
printf("Before: %d, after: %d", all_rows_number, rows_number)
```


```{r}
summary(data)
```


